Fields COVID-19 dataset exploration

### 2023-01-08 data_cleaning/Data_cleaning_and_covariates_Jan_05.qmd
Desgracia

Next, we are interested in analyzing the geographical distribution of the answers the participants within the geographical areas defined by the Association of Municipalities from Ontario. There are two parts to the geographical analysis:

@@

>>>>

Next, we are interested in analyzing the geographical distribution of the answers the participants within the geographical areas defined by the Association of Municipalities from Ontario.

**Update: the populations by census division/city were found on Jan 8, 2023 (from https://www12.statcan.gc.ca/census-recensement/2021/dp-pd/prof/index.cfm?Lang=E). The correction will be done using these numbers instead. The numbers can be found in `census_population_by_division.csv` in `data` directory.**

There are two parts to the geographical analysis:

@@

**This section needs to be modified as the correction has been done by geographica area on Jan 8, 2023**
